\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/intro.tex
minor

\begin{figure}
\begin{lstlisting}[language=C]
uint w[30] = input1(); uint b = input1();
uint x[30] = input2();
uint acc = 0;
for i in [0:30] { acc =  acc + (w[i] * x[i]); }
output((acc > b) ? 1 : 0)
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:introexample}
\end{figure}

\subsubsection*{Ease of programming} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, Figure~\ref{fig:introexample}
shows an \tool source
program for $w^Tx >b$.
%
%\vspace{0.2cm}
%
%\vspace{0.2cm}
The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with its usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

@@

\subsubsection*{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
  and some have also developed tools that allow writing such combinations
  (e.g. \cite{bogdanov,lone,tasty}). Kerschbaum et al.~\cite{autoS}
  even provide a scheme to automatically select optimal protocols
  for sub-compuations. However, as Demmler et al.~\cite{aby} note, due
  to high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. Additionally, these prior works neither have a
developer-friendly language, nor do they formalize their type system
and operational semantics, and show them to be consistent.
We provide a detailed survey of related work in \sectionref{related}.

>>>>

\begin{figure}
\begin{lstlisting}[language=C]
uint w[30] = input1(); uint b = input1();
uint x[30] = input2();
uint acc = 0;
for i in [0:30] { acc =  acc + (w[i] * x[i]); }
output((acc > b) ? 1 : 0)
\end{lstlisting}
\caption{\tool code for $w^Tx >b$}
\label{fig:ex-sml}
\end{figure}

\subsubsection*{Ease of programming} \tool source programs are ideal
functionalities that describe ``what'' computation needs to be done,
rather than ``how'' to do it. In particular, the programmer writes the
high-level computation without thinking about the underlying
cryptographic details. For example, Figure~\ref{fig:ex-sml}
shows an \tool source
program for $w^Tx >b$.
%
%\vspace{0.2cm}
%
%\vspace{0.2cm}
The program is quite similar to what a programmer might
write in C++ or Java. The simplicity of the
language comes with its usual benefits: it is easily accessible to the
developers, there are fewer avenues for making mistakes, developers
don't bear the burden of getting cryptographic details right, and it
is easy to maintain and modify the programs. Needless to say,
frameworks that expose low-level circuit APIs to the programmer do not
enjoy these benefits.

@@

\subsubsection*{Related Work}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} note, due
 to high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries and lack formal semantics.
%Can be added to related work
% Kerschbaum et al.~\cite{autoS}
%provide a scheme to automatically assign homomorphic encryption or
%garbled circuits to each operators in a computation that has been expressed as a sequence of dyadic operations.
%They conjecture that the problem is NP hard and gave a linear programming based solution
%as well as a quadratic time greedy heuristic. \tool  uses a simpler constant time heuristic
%to assign arithmetic secret sharing or garbled circuits to sub-computations
%in a richer language with control flow statements such as loops and branches.
 We provide a detailed survey of related
work in \sectionref{related}.
